---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
options(width = 90)
options(max.print = 200)
```

# pkgsearch

> Get/search CRAN metadata about packages by keyword, popularity, recent activity, package name and more.

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Linux Build Status](https://travis-ci.org/r-hub/pkgsearch.svg?branch=master)](https://travis-ci.org/r-hub/pkgsearch)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/r-hub/pkgsearch?svg=true)](https://ci.appveyor.com/project/gaborcsardi/pkgsearch)
[![CRAN status](https://www.r-pkg.org/badges/version/pkgsearch)](https://cran.r-project.org/package=pkgsearch)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/pkgsearch)](https://www.r-pkg.org/pkg/pkgsearch)
[![Coverage status](https://codecov.io/gh/r-hub/pkgsearch/branch/master/graph/badge.svg)](https://codecov.io/github/r-hub/pkgsearch?branch=master)
<!-- badges: end -->

`pkgsearch` uses R-hub web services that munge CRAN metadata and let you access it through several lenses.

## Search relevant packages

Do you need to find packages solving a particular problem, e.g. "permutation test"? 

```{r search}
library("pkgsearch")
pkg_search("permutation test")
```

## Get package metadata

Do you want to find the dependencies the first versions of `testthat` had and when each of these versions was released? 

```{r history}
cran_package_history("testthat")
```

## Discover packages

Do you want to know what packages are trending on CRAN these days? `pkgsearch` can help!

```{r trend}
cran_trending()
cran_top_downloaded()
```

## Keep up with CRAN

Are you curious about the latest releases or archivals?

```{r}
cran_events()
```

## More info

Find out more in [the documentation website](https://r-hub.github.io/pkgsearch/), in particular the [function reference](https://r-hub.github.io/pkgsearch/reference/index.html) and [the vignette about search features](https://r-hub.github.io/pkgsearch/articles/search.html).

## Installation

Install the latest pkgsearch release from CRAN:

```r
install.packages("pkgsearch")
```

## License

MIT @ [Gábor Csárdi](https://github.com/gaborcsardi),
      [RStudio](https://github.com/rstudio), [R Consortium](https://www.r-consortium.org/).