---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
options(width = 90)
options(max.print = 200)
```

# Search CRAN R Packages and get their metadata

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Linux Build Status](https://travis-ci.org/r-hub/pkgsearch.svg?branch=master)](https://travis-ci.org/r-hub/pkgsearch)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/r-hub/pkgsearch?svg=true)](https://ci.appveyor.com/project/gaborcsardi/pkgsearch)
[![CRAN status](https://www.r-pkg.org/badges/version/pkgsearch)](https://cran.r-project.org/package=pkgsearch)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/pkgsearch)](https://www.r-pkg.org/pkg/pkgsearch)
[![Coverage status](https://codecov.io/gh/r-hub/pkgsearch/branch/master/graph/badge.svg)](https://codecov.io/github/r-hub/pkgsearch?branch=master)
<!-- badges: end -->

The pkgsearch package searches all CRAN packages. It uses a web service,
and a careful weighting that ranks popular packages before less
frequently used ones. The package also has functions to list the new / most recently updated / archived packages, and list all versions of a package.

In this README, read about how `pkgsearch` supports

* [search over all CRAN packages](#search-cran-packages-with-pkgsearch), e.g. by keyword ("colour", "GLM", etc.);

* [extraction of CRAN information](#get-cran-metadata), e.g. releases and archivals.



## Installation

You can install the package from CRAN:

```r
install.packages("pkgsearch")
```

```{r child='vignettes/rmdhunks/search.Rmd'} 
```

```{r child='vignettes/rmdhunks/cran-metadata.Rmd'} 
```

## License

MIT @ [Gábor Csárdi](https://github.com/gaborcsardi),
      [RStudio](https://github.com/rstudio), [R Consortium](https://www.r-consortium.org/).