
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
options(width = 90)
options(max.print = 200)
```

# CRAN package search

[![Linux Build Status](https://travis-ci.org/metacran/pkgsearch.svg?branch=master)](https://travis-ci.org/metacran/pkgsearch)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/metacran/pkgsearch?svg=true)](https://ci.appveyor.com/project/gaborcsardi/pkgsearch)

The `pkgsearch` package searches all CRAN packages. It uses a web service,
and a careful weighting that ranks popular packages before less
frequently used ones.

## Installation

Install the package from github, using `devtools`:

```r
devtools::install_github("metacran/pkgsearch")
```

## Usage

The current API is very minimal, the most important is the `pkg_search()` function,
that does the search:

```{r}
library(pkgsearch)
pkg_search("C++")
```

By default it returns a short summary of the ten best search hits. Their
details can be printed by using the `format = "long"` option of `pkg_search()`,
or just calling `pkg_search()` again, without any arguments, after a search:


```{r}
pkg_search()
```

The `more()` function can be used to display the next batch of search hits,
batches contain ten packages by default:

```{r}
pkg_search("google")
```

```{r}
more()
```

```{r}
more()
```
