
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
options(width = 90)
options(max.print = 200)
```

# CRAN package search

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Linux Build Status](https://travis-ci.org/metacran/pkgsearch.svg?branch=master)](https://travis-ci.org/metacran/pkgsearch)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/metacran/pkgsearch?svg=true)](https://ci.appveyor.com/project/gaborcsardi/pkgsearch)
[![CRAN status](https://www.r-pkg.org/badges/version/pkgsearch)](https://cran.r-project.org/package=pkgsearch)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/pkgsearch)](https://www.r-pkg.org/pkg/pkgsearch)
[![Coverage status](https://codecov.io/gh/metacran/pkgsearch/branch/master/graph/badge.svg)](https://codecov.io/github/metacran/pkgsearch?branch=master)

The pkgsearch package searches all CRAN packages. It uses a web service,
and a careful weighting that ranks popular packages before less
frequently used ones.

## Installation

Once released, you can install the package from CRAN:

```r
install.packages("pkgsearch")
```

## Usage

The current API is very minimal, the most important is the `pkg_search()` function,
that does the search:

```{r}
library(pkgsearch)
pkg_search("C++")
```

By default it returns a short summary of the ten best search hits. Their
details can be printed by using the `format = "long"` option of `pkg_search()`,
or just calling `pkg_search()` again, without any arguments, after a search:


```{r}
pkg_search()
```

The `more()` function can be used to display the next batch of search hits,
batches contain ten packages by default:

```{r}
pkg_search("google")
```

```{r}
more()
```

```{r}
more()
```
